The simulated annealing algorithm of GMSE

### 2022-04-16 notebook/cran_vignettes/SI9.Rmd
Data on the simulated annealing versus genetic algorithm

```{r, echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Comparison of stakeholder culls (a metric of decision-making performance) across different simulation times when running a genetic algorithm versus a simulated annealing algorithm in GMSE. Each point represents a unique simulation of 40 time steps run at a specific number of genetic algorithm generations (ga_min) or simulated annealing iterations (kmx)."}
ga_repl <- read.csv("data/SI9/genetic_algorithm_reps.csv");
sa_repl <- read.csv("data/SI9/sim_annealing_reps.csv");
GA_summ <- read.csv("data/SI9/GA_summary.csv");
SA_summ <- read.csv("data/SI9/SA_summary.csv");
gafit   <- read.csv("data/SI9/gafit.csv");
safit   <- read.csv("data/SI9/safit.csv");
plot(x = SA_summ[,2], SA_summ[,4], xlim = c(7, 19), ylim = c(0, 1000),
     xlab = "Simulation time (sec)", ylab = "Stakeholder culls", cex = 1.5,
     pch = 20, col = "red");
points(x = GA_summ[,2], GA_summ[,4], cex = 1.5, pch = 20, col = "black");
legend(x = 12, y = 200, fill = c("black", "red"), cex = 1.25,
       legend = c("Genetic Algorithm", "Simulated Annealing"));
```

@@

User fitness increase by iteration or generation
--------------------------------------------------------------------------------

@@

```{r, eval = FALSE}
sim <- gmse(time_max = 40, land_ownership = TRUE, scaring = FALSE, 
            culling = TRUE, castration = FALSE, help_offspring = FALSE, 
            tend_crops = FALSE, kill_crops = FALSE, plotting = FALSE,
            ga_seedrep = 0, user_annealing = FALSE, mana_annealing = FALSE,
            kmax_annealing = 40, ga_mingen = 40);
```

@@

```{r, echo = FALSE, eval = TRUE, fig.cap = "Comparison of user fitness across different genetic algorithm generation numbers or simulated annealing iteration numbers in GMSE when users only have culling available as an action."}
# Only culling
plot(x = gafit[,1], y = gafit[,2], type = "l", lwd = 2, cex = 0.5,
     col = "black", pch = 20, ylim = c(1800, 3600), 
     xlab = "Generation / Iteration", ylab = "Scaled user fitness", xlim = c(1, 39));
points(x = safit[,1], y = safit[,2], type = "l", lwd = 2, cex = 0.5,
     col = "red", pch = 20);
legend(x = 22, y = 2300, fill = c("black", "red"),
       legend = c("Genetic Algorithm", "Simulated Annealing"));
text(x = 30, y = 3500, labels = "Only Culling", cex = 1.25);
```

@@

```{r, echo = FALSE, eval = TRUE, fig.cap = "Comparison of user fitness across different genetic algorithm generation numbers or simulated annealing iteration numbers in GMSE when users have all actions available to them."}
plot(x = gafit[,1], y = gafit[,3], type = "l", lwd = 2, cex = 0.5,
     col = "black", pch = 20, ylim = c(1200, 4800), 
     xlab = "Generation / Iteration", ylab = "Scaled user fitness", xlim = c(1, 39));
points(x = safit[,1], y = safit[,3], type = "l", lwd = 2, cex = 0.5,
     col = "red", pch = 20);
legend(x = 0, y = 4900, fill = c("black", "red"),
       legend = c("Genetic Algorithm", "Simulated Anealing"));
text(x = 25, y = 1600, labels = "All possible user actions", cex = 1.5);
```

@@

```{r, echo = FALSE, eval = TRUE, fig.cap = "Comparison of manager fitness across different genetic algorithm generation numbers or simulated annealing iteration numbers in GMSE when managers only have culling available as a policy option."}
# Only culling
plot(x = gafit[,1], y = gafit[,4], type = "l", lwd = 2, cex = 0.5,
     col = "black", pch = 20, ylim = c(0, 74000), 
     xlab = "Generation / Iteration", ylab = "Scaled user fitness", xlim = c(1, 39));
points(x = safit[,1], y = safit[,4], type = "l", lwd = 2, cex = 0.5,
     col = "red", pch = 20);
legend(x = 22, y = 20000, fill = c("black", "red"),
       legend = c("Genetic Algorithm", "Simulated Annealing"));
text(x = 10, y = 3500, labels = "Only Culling", cex = 1.25);
```

@@

```{r, echo = FALSE, eval = TRUE, fig.cap = "Comparison of manager fitness across different genetic algorithm generation numbers or simulated annealing iteration numbers in GMSE when managers have all policy options available to them."}
plot(x = gafit[,1], y = gafit[,5], type = "l", lwd = 2, cex = 0.5,
     col = "black", pch = 20, ylim = c(300000, 2000000), 
     xlab = "Generation / Iteration", ylab = "Scaled user fitness", xlim = c(1, 39));
points(x = safit[,1], y = safit[,5], type = "l", lwd = 2, cex = 0.5,
     col = "red", pch = 20);
legend(x = 0, y = 1300000, fill = c("black", "red"),
       legend = c("Genetic Algorithm", "Simulated Anealing"));
text(x = 28, y = 1000000, labels = "All possible user actions", cex = 1.5);
```

>>>>

```{r, echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Comparison of stakeholder culls (a metric of decision-making performance) across different simulation times when running a genetic algorithm versus a simulated annealing algorithm in GMSE. Each point represents a unique simulation of 40 time steps run at a specific number of genetic algorithm generations (ga_min) or simulated annealing iterations (kmx)."}
ga_repl <- read.csv("data/SI9/genetic_algorithm_reps.csv");
sa_repl <- read.csv("data/SI9/sim_annealing_reps.csv");
GA_summ <- read.csv("data/SI9/GA_summary.csv");
SA_summ <- read.csv("data/SI9/SA_summary.csv");
gafit   <- read.csv("data/SI9/gafit.csv");
safit   <- read.csv("data/SI9/safit.csv");
ga_fitness_user_cull <- read.csv("data/SI9/ga_fitness_user_cull.csv");
ga_fitness_user_all  <- read.csv("data/SI9/ga_fitness_user_all.csv");
ga_fitness_mana_cull <- read.csv("data/SI9/ga_fitness_mana_cull.csv");
ga_fitness_mana_all  <- read.csv("data/SI9/ga_fitness_mana_all.csv");
sa_fitness_user_cull <- read.csv("data/SI9/sa_fitness_user_cull.csv");
sa_fitness_user_all  <- read.csv("data/SI9/sa_fitness_user_all.csv");
sa_fitness_mana_cull <- read.csv("data/SI9/sa_fitness_mana_cull.csv");
sa_fitness_mana_all  <- read.csv("data/SI9/sa_fitness_mana_all.csv");
plot(x = SA_summ[,2], SA_summ[,4], xlim = c(7, 19), ylim = c(0, 1000),
     xlab = "Simulation time (sec)", ylab = "Stakeholder culls", cex = 1.5,
     pch = 20, col = "red");
points(x = GA_summ[,2], GA_summ[,4], cex = 1.5, pch = 20, col = "black");
legend(x = 12, y = 200, fill = c("black", "red"), cex = 1.25,
       legend = c("Genetic Algorithm", "Simulated Annealing"));
```

@@

User fitness increase fitness function call
--------------------------------------------------------------------------------

@@

```{r, eval = FALSE}
sim <- gmse(time_max = 40, land_ownership = TRUE, scaring = FALSE, 
            culling = TRUE, castration = FALSE, help_offspring = FALSE, 
            feeding = FALSE, tend_crops = FALSE, kill_crops = FALSE, 
            plotting = FALSE, ga_seedrep = 0, user_annealing = FALSE, 
            mana_annealing = FALSE, kmax_annealing = 40, ga_mingen = 40);
```

@@

```{r, echo = FALSE, eval = TRUE, fig.cap = "Comparison of user fitness across different genetic algorithm generation numbers or simulated annealing iteration numbers in GMSE when users only have culling available as an action."}
# Only culling
plot(x = ga_fitness_user_cull[,1], y = ga_fitness_user_cull[,2], type = "l", 
     lwd = 2, cex = 0.5, col = "black", pch = 20, ylim = c(1000, 4000), 
     xlab = "Calls to fitness function", ylab = "Scaled user fitness", 
     xlim = c(0, 4000));
points(x = sa_fitness_user_cull[,1], y = sa_fitness_user_cull[,2], 
       type = "l", lwd = 2, cex = 0.5, col = "red", pch = 20);
legend(x = 2500, y = 1700, fill = c("black", "red"),
       legend = c("Genetic Algorithm", "Simulated Annealing"));
text(x = 2000, y = 3900, labels = "Only Culling", cex = 1.25);
```

@@

```{r, echo = FALSE, eval = TRUE, fig.cap = "Comparison of user fitness across different genetic algorithm generation numbers or simulated annealing iteration numbers in GMSE when users have all actions available to them."}
# All options
plot(x = ga_fitness_user_all[1:40,1], y = ga_fitness_user_all[1:40,2], type = "l", 
     lwd = 2, cex = 0.5, col = "black", pch = 20, ylim = c(0, 5000), 
     xlab = "Calls to fitness function", ylab = "Scaled user fitness", xlim = c(0, 4000));
points(x = sa_fitness_user_all[,1], y = sa_fitness_user_cull[,2], 
       type = "l", lwd = 2, cex = 0.5, col = "red", pch = 20);
legend(x = 0, y = 5000, fill = c("black", "red"),
       legend = c("Genetic Algorithm", "Simulated Annealing"));
text(x = 2500, y = 5000, labels = "All actions", cex = 1.25);
```

@@

```{r, echo = FALSE, eval = TRUE, fig.cap = "Comparison of manager fitness across different genetic algorithm generation numbers or simulated annealing iteration numbers in GMSE when managers only have culling available as a policy option."}
# Only culling
ofst <- 9726594;
plot(x = ga_fitness_mana_cull[,1], y = ga_fitness_mana_cull[,2] - ofst, 
     type = "l",  lwd = 2, cex = 0.5, col = "black", pch = 20, 
     ylim = c(50000, 170000), xlab = "Calls to fitness function", 
     ylab = "Scaled manager fitness", xlim = c(0, 4000));
points(x = sa_fitness_mana_cull[,1], y = sa_fitness_mana_cull[,2] - ofst,
       type = "l", lwd = 2, cex = 0.5, col = "red", pch = 20);
legend(x = 2500, y = 80000, fill = c("black", "red"),
       legend = c("Genetic Algorithm", "Simulated Annealing"));
text(x = 500, y = 165000, labels = "Only Culling", cex = 1.25);
```

@@

```{r, echo = FALSE, eval = TRUE, fig.cap = "Comparison of manager fitness across different genetic algorithm generation numbers or simulated annealing iteration numbers in GMSE when managers have all policy options available to them."}
# All
ofst <- 9035476;
plot(x = ga_fitness_mana_all[,1], y = ga_fitness_mana_all[,2] - ofst, 
     type = "l",  lwd = 2, cex = 0.5, col = "black", pch = 20, 
     ylim = c(500000, 900000), xlab = "Calls to fitness function", 
     ylab = "Scaled manager fitness", xlim = c(0, 4000));
points(x = sa_fitness_mana_all[,1], y = sa_fitness_mana_all[,2] - ofst,
       type = "l", lwd = 2, cex = 0.5, col = "red", pch = 20);
legend(x = 0, y = 750000, fill = c("black", "red"),
       legend = c("Genetic Algorithm", "Simulated Annealing"));
text(x = 2000, y = 900000, labels = "All actions", cex = 1.25);
```
